Hou10ni

### 2017-10-06 hou10ni/Tutorial/hou10ni_profile.tex
Hou10ni: new scripts + Papi

\begin{cverbatim}
export TAU_MAKEFILE=$TAU_DIR/Makefile.
export TAU_OPTIONS='-optPdtF95Opts="-R free" -optVerbose'

@@

\noindent $\rightarrow$ Press "t" to change the compiler and chose \texttt{tau\_f90.sh}. Then you can tape \texttt{make} and launch the application.

\begin{cverbatim}
make
cd .. 
mpirun -np 4 tau_exec -T mpi  build/hou10ni.out < HPC4E.dat
\end{cverbatim}

>>>>

\begin{cverbatim}
export TAU_MAKEFILE=$TAU_DIR/Makefile.tau...  (ex.: Makefile.tau-icpc-mpi-pdt)
export TAU_OPTIONS='-optPdtF95Opts="-R free" -optVerbose'

@@

\noindent $\rightarrow$ Press "t" to change the compiler and chose \texttt{tau\_f90.sh} and add TAU lib\\
 (e.g., \texttt{/home/esaillard/TOOLS/TAU/tau-2.26/build/x86\_64/lib/libTAU\_traceinput-icpc-mpi-pdt.a}) in the linker flag. Then you can tape \texttt{make} and launch the application.

\begin{cverbatim}
make
cd .. 
mpirun -np 4 tau_exec -T mpi  -io -memory build/hou10ni.out < HPC4E.dat
\end{cverbatim}
